gij bent 2

### 2025-09-28 paper/paper.qmd
Stylise emmeans
Explain behaviour reversal better

We see that the distinction between users who are thought to be male and users who are thought to be female does not reach the significance threshold. Therefore, the differences which we discussed in @sec-group-variation are not different enough to the degree that they are actually distinct. Still, the fact that the *tendency* is clearly there is still interesting, and the reversal of the extreme values of course still holds.

@@

In addition, we wanted to know whether there are also differences *between* the non-Brabant dialact areas. To investigate this, we ran a post-hoc analysis through emmeans [@emmeans]. In this post-hoc analysis, we check for each dialect area pair whether there are significant differences in individual variation between the two. We see in @tbl-posthoc-test that there are *no* further differences between the non-Brabant dialect areas. Our assessment of the two variation profiles was thus correct.

>>>>

We see that the distinction between users who are thought to be male and users who are thought to be female does not reach the significance threshold. Therefore, the differences which we discussed in @sec-group-variation are not different enough to the degree that they are actually distinct. Still, the fact that the *tendency* is clearly there is still interesting, and the idea that individual behaviour can be the reverse of a general trend of course still holds.

@@

In addition, we wanted to know whether there are also differences *between* the non-Brabant dialact areas. To investigate this, we ran a post-hoc analysis through `emmeans` [@emmeans]. In this post-hoc analysis, we check for each dialect area pair whether there are significant differences in individual variation between the two. We see in @tbl-posthoc-test that there are *no* further differences between the non-Brabant dialect areas. Our assessment of the two variation profiles was thus correct.
